### 2019-08-08 tables/03_model_summary.Rmd
output model summary table

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
```

```{r summary_table, eval=TRUE}
library(kableExtra)
library(dplyr)
library(magrittr)
library(stringr)

# setwd("tables")
dt <- read.csv("../data/mcmc/model_r2.csv", 
                     stringsAsFactors = FALSE)

options(knitr.kable.NA = "-")  
dplyr::filter(dt, str_detect(Model, "tp")) %>%
  dplyr::select(-Model) %>%
  dplyr::rename("$R^2$" = Estimate) %>%
  knitr::kable(digits = 2, format = "markdown", caption = "TP Model R2")
```

\pagebreak
```{r tn_results}
dplyr::filter(dt, str_detect(Model, "tn")) %>%
  dplyr::select(-Model) %>%
  dplyr::rename("$R^2$" = Estimate) %>%
  knitr::kable(digits = 2, format = "markdown", caption = "TN Model R2")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
# setwd("tables")
source("../scripts/99_utils.R")
```

```{r summary_table, eval=TRUE}
# setwd("tables")
re_brms <- readRDS("../data/mcmc/re_brms.rds")

r2_re <- dplyr::bind_rows(
  lapply(re_brms, function(x) data.frame(brms::bayes_R2(x))))
r2_re$term <- unlist(lapply(re_brms, 
                                function(x) get_re_text(as.character(x$formula)[1])))
r2_re$response <- c(rep("tp", nrow(r2_re) / 2), rep("tn", nrow(r2_re) / 2))
r2_re <- dplyr::filter(r2_re, term != "rowvcropvpct")

sort_loo <- function(x){
  x_df       <- as.data.frame(x)
  x_df$index <- row.names(x_df)
  x_df$index <- as.numeric(stringr::str_extract(x_df$index, "\\d+"))
  arrange(x_df, index)
}

loo_re <- rbind(
  sort_loo(loo_compare(loo(re_brms[[1]]),
                       loo(re_brms[[3]]), loo(re_brms[[4]]),
                       loo(re_brms[[5]]), 
                       loo(re_brms[[6]]))),
  sort_loo(loo_compare(loo(re_brms[[7]]),
                       loo(re_brms[[9]]), loo(re_brms[[10]]),
                       loo(re_brms[[11]]), 
                       loo(re_brms[[12]])))
  ) %>%
  arrange(index)

dt           <- r2_re
dt$elpd_diff <- loo_re$elpd_diff
dt <- dplyr::select(dt, 
                    response, term, r2 = Estimate, elpd_diff)
dt <- dt[order(dt$response, dt$elpd_diff, decreasing = c(TRUE, FALSE)),]

options(knitr.kable.NA = "-")  
dt %>%
  # dplyr::filter(str_detect(response, "tp")) %>%
  # dplyr::select(-response) %>%
  dplyr::rename("$R^2$" = r2) %>%
  knitr::kable(digits = 2, format = "markdown", caption = "TP Model R2")
```

\pagebreak
```{r tn_results, eval=FALSE}
dplyr::filter(dt, str_detect(response, "tn")) %>%
  dplyr::select(-response) %>%
  dplyr::rename("$R^2$" = r2) %>%
  knitr::kable(digits = 2, format = "markdown", caption = "TN Model R2")
```
